Effects of rarefaction

### 2021-04-19 analysis/rev_prototyping/old/rarefaction.Rmd

@@

@@

overall_results

@@

ggplot(filter(adjusted_comparison, log_nparts_TRUE > log(20), log_nparts_FALSE > log(20)), aes(mean_po_comparison_percentile_FALSE, mean_po_comparison_percentile_TRUE)) +
  geom_point(alpha = .1) +
  theme_bw() +
  geom_abline(intercept = 0, slope = 1, color = "green") +
  facet_wrap(vars(dat))

>>>>

theme_set(theme_bw())

@@

overall_results_long <- overall_results %>%
  tidyr::pivot_longer(-dat, names_to = "varname", values_to = "proportion") %>%
  group_by_all() %>%
  mutate(direction = unlist(strsplit(varname, "_"))[[1]],
         metric = unlist(strsplit(varname, "_"))[[2]],
         adjusted = unlist(strsplit(varname, "_"))[[3]]) %>%
  ungroup() %>%
  mutate(dir_metric = paste(direction, metric, sep= "_"))

@@

@@

ggplot(filter(adjusted_comparison, log_nparts_TRUE > log(20), log_nparts_FALSE > log(20)), aes(mean_po_comparison_percentile_FALSE, mean_po_comparison_percentile_TRUE)) +
  geom_point(alpha = .1) +
  theme_bw() +
  geom_abline(intercept = 0, slope = 1, color = "green") +
  facet_wrap(vars(dat)) 
```

```{r, fig.dim = c(8,8)}

overall_results
ggplot(overall_results_long, aes(adjusted, proportion, color = adjusted)) +
  geom_point() +
  facet_grid(cols = vars(dir_metric), rows = vars(dat), scales = "free", switch = "y") +
  theme(legend.position = "top")
